\documentclass[12pt]{article}
\usepackage[paperheight=240mm, paperwidth=170mm, tmargin=25mm, bmargin=20mm, rmargin=20mm, lmargin=20mm]{geometry}

%\usepackage{fancyhdr}
\usepackage{wallpaper}
\usepackage[T1]{fontenc}
\renewcommand{\familydefault}{\sfdefault} 

\title{\textbf{\Large Personalized Schedules for Invasive\\Diagnostic Tests}\\\normalsize With Applications in Surveillance of Chronic Non-Communicable Diseases \vspace{-20mm}}
\date{}
\pagenumbering{gobble}


\begin{document}
\maketitle
\begin{center}
\textit{\large Gepersonaliseerde Schema's voor Invasieve\\ Diagnostische Testen\\\normalsize met Toepassingen voor het Monitoren van Chronische Niet-overdraagbare Ziekten}\\
\vspace{10mm}
\textbf{\large{Proefschrift}}\\
\vspace{10mm}
ter verkrijging van de graad van doctor aan de\\
Erasmus Universiteit Rotterdam\\
op gezag van de\\
rector magnificus\\
\vspace{10mm}
Prof.dr. R.C.M.E. Engels\\
\vspace{10mm}
en volgens besluit van het College voor Promoties.\\
De openbare verdediging zal plaatsvinden op\\
16 September 2020 om 9:30 uur\\
\vspace{10mm}
door\\
\vspace{10mm}
Anirudh Tomer\\
geboren te Jorhat, India. 
\end{center}
\ThisLLCornerWallPaper{0.45}{eur_line.pdf}
\ThisLRCornerWallPaper{0.4}{eur_logo.pdf}

%Reverse page
\clearpage
\begin{flushleft}
\textbf{\large{Promotiecommissie:}}\\
\vspace{10mm}
\textbf{Promotoren:} \hspace{1.5mm} Prof. dr. D. Rizopoulos\\
\hspace{28mm} Prof. dr. E. W. Steyerberg\\
\vspace{10mm}
\textbf{Overige leden:} Prof. dr. ir. E. H. Boersma\\
\hspace{28mm} Prof. dr. M. J. Roobol\\
\hspace{28mm} Prof. dr. H. Putter\\
\end{flushleft}
\vspace*{\fill}

\noindent The research described in this thesis was supported by Nederlandse Organisatie voor Wetenschappelijk Onderzoek VIDI grant nr. 016.146.301, and Erasmus University Medical Center funding.\\

\noindent Support by the PRIAS consortium for enabling this research project is gratefully acknowledged.\\

\noindent Support by the Erasmus University Medical Center's Cancer Computational Biology Center for giving access to their IT-infrastructure and software that was used for the computations and data analysis in this research is gratefully acknowledged.\\

\noindent Part of this research was carried out on the Dutch national e-infrastructure with the support of SURF Cooperative.\\
\end{document}