\chapter[Personalized Biopsy Schedules Based on Risk of Gleason Upgrading for Low-Risk Prostate Cancer Active Surveillance Patients][Upgrading-risk Based Personalized Biopsy Schedules]{Personalized Biopsy Schedules Based on Risk of Gleason Upgrading for Low-Risk Prostate Cancer Active Surveillance Patients}
\label{c5}

\vspace*{\fill}
\textbf{This chapter is based on the paper}\\
\underline{Tomer, A.}, Nieboer, D., Roobol, M.J., Bjartell, A., Steyerberg, E.W., and Rizopoulos, D. (2020), Personalized Biopsy Schedules Based on Risk of Gleason Upgrading for Low-Risk Prostate Cancer Active Surveillance Patients. \emph{BJU International}. Advance online publication. doi:10.1111/bju.15136

\clearpage
\input{contents/c5/c5_abs}
\clearpage
\input{contents/c5/c5_sec1}
\input{contents/c5/c5_sec2}
\input{contents/c5/c5_sec3}
\input{contents/c5/c5_sec4}
\input{contents/c5/c5_sec5}

\paragraph{Acknowledgements}
We thank Jozien Helleman from the Department of Urology, Erasmus University Medical Center, for coordinating the project. The first and last authors would like to acknowledge support by Nederlandse Organisatie voor Wetenschappelijk Onderzoek (the national research council of the Netherlands) VIDI grant nr. 016.146.301, and Erasmus University Medical Center funding. Part of this work was carried out on the Dutch national e-infrastructure with the support of SURF Cooperative. The authors also thank the Erasmus University Medical Center's Cancer Computational Biology Center for giving access to their IT-infrastructure and software that was used for the computations and data analysis in this study. The PRIAS website is funded by the Prostate Cancer Research Foundation, Rotterdam (SWOP). We would like to thank the PRIAS consortium for enabling this research project. 

This work was supported by the Movember Foundation. The funder did not play any role in the study design, collection, analysis or interpretation of data, or in the drafting of this paper.

\paragraph{Conflicts of Interest}
The authors do not report any conflict of interest, and have nothing to disclose.
\input{contents/c5/c5_gap3members}

\input{contents/c5/c5_appendix}

\clearpage
\bibliographystyle{apalike}
\bibliography{c5_bib}