\chapter[Personalized Decision Making for Biopsies in Prostate Cancer Active Surveillance Programs][Personalized Decision Making]{Personalized Decision Making for Biopsies in Prostate Cancer Active Surveillance Programs}
\label{c3}

\vspace*{\fill}
\textbf{This chapter is based on the paper}\\
\underline{Tomer, A.}, Rizopoulos, D., Nieboer, D., Drost, F.J., Roobol, M.J., and Steyerberg, E.W. (2019). Personalized decision making for biopsies in prostate cancer active surveillance programs. \emph{Medical Decision Making}, 39(5): 499--508. doi: \url{https://doi.org/10.1177/0272989X19861963}

\clearpage
\input{contents/c3/c3_abs}
\clearpage
\input{contents/c3/c3_sec1}
\input{contents/c3/c3_sec2}
\input{contents/c3/c3_sec3}
\input{contents/c3/c3_sec4}

\paragraph{Acknowledgements}
The first and last Authors would like to acknowledge support by Nederlandse Organisatie voor Wetenschappelijk Onderzoek (the national research council of the Netherlands) VIDI grant nr. 016.146.301, and Erasmus University Medical Center funding. The Authors also thank the Erasmus University Medical Center's Cancer Computational Biology Center for giving access to their IT-infrastructure and software that was used for the computations and data analysis in this study. Lastly, we thank Joost Van Rosmalen from the Department of Biostatistics, Erasmus University Medical Center for feedback on the manuscript.

\paragraph{Conflict of Interest}
The Authors declare that there is no conflict of interest.

\input{contents/c3/c3_appendix}

\clearpage
\bibliographystyle{apalike}
\bibliography{c3_bib}