\section{Acknowledgements}
This work was not possible without the blessings, well wishes, and the support of my family. With limited financial resources, my parents made enormous sacrifices to send me to university. It is because of their hard work and strength that I was able to study abroad, stay focused, and write this thesis. I am indebted to my father for his ever-present support for my decisions, to my mother for motivating me to maintain good health, and to my sister for always telling me that she believes in me. I married my lovely wife, Nikhita, in the second year of my PhD. Her love, care, support, and urging me to stop working at 5 pm, saved me from a possible PhD burnout. 

I am grateful to my friends and soul brothers/sisters for listening to both the eureka and frustrating moments of my PhD. Outside work, we hiked, camped, made bonfires and barbecues, and cycled together. Special thanks to Kamen and his parents (Bulgaria), and Karin (Luxembourg) for making me a part of their families. Visiting them gave insights into European culture, and brought me closer to nature and delicious food. Being away from home, my friends turned a `sometimes' mundane PhD routine into a fun life overall.

Isaac Newton said, \emph{`If I have seen further it is by standing on the shoulders of Giants'}. I am no Newton, but I had the fortune of receiving support from two giants of statistics; my advisors Dimitris, and Ewout. I am indebted to them for allowing me to pursue research under their guidance. Dimitris was especially gentle towards my research mistakes. He provided me ample space and time throughout my PhD to understand the subject matter and grow into the researcher role. Truth be told, ideas in this work are only my minor extensions to his novel conceptions. Yet, he was kind enough to give me credit for the work. His humility, compassion, and friendliness towards his PhD students have inspired me to follow in his footsteps in the future. Without his support, I could not have written this thesis timely. I enjoyed statistical discussions with him because he evaluated our ideas based on merit. Dimitris consistently motivated me to leave no stone unturned and emphasized presenting our work in an easy to understand manner. I will carry these lessons for a lifetime.

I am also thankful to my co-advisor Ewout Steyerberg. In our meetings, he spoke with the eloquence of a spiritual guru on a range of topics. His critique on our papers was invariably to the point; his counterexamples exposed weaknesses of our methodologies; and his suggestions were often the hard truth, which is bitter and difficult to absorb, usually frustrating, and yet the right thing to do. Ewout inspired me to be concise in my scientific writing and taught me to prioritize the usefulness of an idea over its mathematical complexity. I am grateful to him for sharing his wisdom whenever we met. 

I was lucky to often collaborate with Daan, a through and through seasoned statistician. I am grateful to him for assisting me formulate response letters for reviewers, prediction modeling, and expert advice on prostate cancer surveillance. My kind regards and best wishes to my colleagues from the Department of Urology. Although mostly we know each other only by face, they made me feel welcome whenever I visited them with questions.

I am grateful to all of my colleagues for sharing their knowledge during my PhD. Greg went above and beyond to help me even before I started. Elrozy and Joost always responded to my knocks on their office doors with a smile. They never even asked me to come later. Talking with them over lunch and tea lowered my work-related stress. I am indebted to both of them. Joost, thank you for providing useful advice for administrative matters related to my stay in the Netherlands. Special thanks to Paloma and Floor for being great friends. Paloma and Dino, your Bolivian dishes are delicious. Thank you for the evening walks and smiles. I am glad Nikki and I could share our cultures and cuisines with Floor and Paloma. Floor took extra efforts to make my wife and I feel welcome in the Netherlands. She is one of the kindest people I have met. I wish everyone gets a Dutch friend like her. Lastly, I would like to thank Eline for being a true friend in need. I do not have words to express my gratitude for the countless number of times she helped me in dire situations outside work. I may not be able to return her favors, but I promise to pay them forward to others.

In the end, I am grateful to the almighty for keeping me in good health, for giving me the means to see mountains up close, eat tasty food from around the world, and for showing miracles whenever I almost gave up.