\section{PhD Portfolio}
\autorows[0.75\textwidth]{l}{2}{l}{ PhD Candidate:, Anirudh Tomer, 
Department:, Department of Biostatistics, 
 , Erasmus MC Rotterdam the Netherlands,
PhD Period:, Sep 2016 -- Aug 2020,
Promoters:, Prof. dr. Dimitris Rizopoulos,
 , Prof. dr. Ewout W. Steyerberg}

\subsection*{Publications}
\noindent \underline{Tomer, A.}, Nieboer, D., Roobol, M.J., Steyerberg, E.W., and Rizopoulos, D. (2019), Personalized schedules for surveillance of low-risk prostate cancer patients. \emph{Biometrics}, 75: 153--162.\\

\noindent \underline{Tomer, A.}, Rizopoulos, D., Nieboer, D., Drost, F.J., Roobol, M.J., and Steyerberg, E.W. (2019). Personalized decision making for biopsies in prostate cancer active surveillance programs. \emph{Medical Decision Making}, 39(5): 499--508.\\

\noindent \underline{Tomer, A.}, Nieboer, D., Roobol, M.J., Steyerberg, E.W., and Rizopoulos, D. (2020), Personalized schedules for burdensome surveillance tests. Submitted to \emph{Journal of the American Statistical Association}\\

\noindent \underline{Tomer, A.}, Nieboer, D., Roobol, M.J., Bjartell, A., Steyerberg, E.W., and Rizopoulos, D. (2020), Personalized Biopsy Schedules Based on Risk of Gleason Upgrading for Low-Risk Prostate Cancer Active Surveillance Patients. \emph{BJU International}. Advance online publication. doi:10.1111/bju.15136\\

\noindent Schuurman, A.S., \underline{Tomer, A.}, Akkerhuis, K.M., Brugts, J.J., Constantinescu, A.A., van Ramshorst, J., Umans, V.A., Boersma, E., Rizopoulos, D., and Kardys, I. (2020). Personalized screening intervals for measurement of N-terminal pro-B-type natriuretic peptide improve efficiency of prognostication in patients with chronic heart failure. \emph{European Journal of Preventive Cardiology}. Advance online publication. doi:10.1177/2047487320922639\\ 

\noindent Papageorgiou, G., Mauff, K., \underline{Tomer, A.}, and Rizopoulos, D. (2019). An overview of joint modeling of time-to-event and longitudinal outcomes. \emph{Annual Review of Statistics and Its Application}, 6(1): 223--240.\\

\noindent Nieboer, D., \underline{Tomer, A.}, Rizopoulos, D., Roobol, M.J., and Steyerberg, E.W. (2018). Active surveillance: a review of risk-based, dynamic monitoring. \emph{Translational Andrology and Urology}, 7(1), 106--115.\\

\small
\begin{ctabular}[l]{llr}
\toprule
\textbf{1. PhD Training} & year & ECTS\\
\midrule
\textbf{International Conferences} & & \\
29th IBS Conference, Barcelona, Spain & 2018 & 1.5\\
(\emph{runner-up best oral presentation}) & & \\
10th EMR-IBS Conference, Jerusalem, Israel & 2018 & 1.0\\
(\emph{student award for attending conference}) & & \\
40th ISCB Conference, Leuven, Belgium & 2019 & 1.0\\
35th EAU Conference, Netherlands  & 2020 & 1.0\\ 
\\
\textbf{Seminars and Workshops (the Netherlands)} & & \\
Fortnightly Biostatistics CQM Seminar & 2016 -- 2020 & 3.0\\
Yearly Erasmus Statistics Day & 2016 -- 2020 & 1.0\\
Erasmus MC -- LUMC Joint Statistics Meeting & 2016 & 0.2\\
BMS-ANed PhD Day & 2017 & 0.2\\
BMS-ANed Spring Meeting & 2018 & 0.2\\
VVSOR R Shiny Workshop (\emph{presenter}) & 2019 & 1.0\\
BMS-ANed PhD Day & 2019 & 0.2\\
\\
\textbf{Courses} & & \\
Research Integrity & 2017 & 0.3\\
\\
\midrule
\textbf{2. Teaching and Work Experience} & year & ECTS\\
\midrule
\textbf{Teaching Assistant} & & \\
SPSS Practicals (VO1) & 2016 -- 2020 & 1.0\\
Biostatistical Methods II (EP03) & 2016 -- 2020 & 1.0\\
Repeated Measurements (CE08) & 2016 -- 2020 & 1.0\\
\\
\textbf{CPO Consultant} & & \\
Erasmus MC CPO Statistical Consultant (\emph{65 clients}) & 2016 -- 2020 & 10.0\\
\bottomrule
\end{ctabular}
\normalsize